Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-18 paper-2023-acsos-pulverization.tex
Add simulation screenshot
Replace MQTT with AMQP protocol

The configuration produced by the \ac{dsl} needs a platform that instructs the system on the way actual communication needs to be performed.
%
In our current implementation,
we provide out of the box a JVM platform based on the MQTT protocol
supporting both intra- and inter-device communication.
%
The platform also feature an optimization for pulverized components of the same logical device ending up running on the same host:
as it would be expected,
they would communicate directly by sharing memory,
without the need to go through (de)serialisation processes and networking.
\meta{NICOLAS please check if the last sentence is true, if so remove this comment}
%
For the large scale experiment,
we implemented a second platform,
this time to comply with the requirements of the simulation engine we used.
%
The implementation required little effort,
and it has been made available as part of the evaluation repositories.

@@

This example has been used as a real-world testbed driving our experimental implementation.
%
For the sake of brevity,
we do not report the entire configuration in this manuscript, but it is available in the companion artifact~\cite{TBD}
\meta{
    NICOLAS please replace TBD with the artifact citation from zenodo. Use doi2bib to get the bibtex entry.
}
for those willing to exercise the whole system.
%
To simplify testing we also provide,
in the same artifact,
a simulation of the system where every device is containerized.

@@

>>>>

The configuration produced by the \ac{dsl} needs a platform that instructs the system on the way actual communication needs to be performed.
%
In our current implementation,
we provide out of the box a JVM platform based on the AMQP protocol leveraging RabbitMQ,
supporting both intra- and inter-device communication.
%
The platform also feature an optimization for pulverized components of the same logical device ending up running on the same host:
as it would be expected,
they would communicate directly by sharing memory,
without the need to go through (de)serialisation processes and networking.
%
For the large scale experiment,
we implemented a second platform,
this time to comply with the requirements of the simulation engine we used.
%
The implementation required little effort,
and it has been made available as part of the evaluation repositories.

@@

This example has been used as a real-world testbed driving our experimental implementation.
%
For the sake of brevity,
we do not report the entire configuration in this manuscript, but it is available in the companion artifact~\cite{https://doi.org/10.5281/zenodo.7933160}
% \meta{
%     NICOLAS please replace TBD with the artifact citation from zenodo. Use doi2bib to get the bibtex entry.
% }
for those willing to exercise the whole system.
%
To simplify testing we also provide,
in the same artifact,
a simulation of the system where every device is containerized.

@@

\begin{figure}[ht]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\linewidth]{figures/simulation-screenshot.png}
    \end{minipage}
    \caption{TODO}
    \label{fig:simulation-screenshot}   
\end{figure}
